---
title: "hw4"
author: "Alexandra Bushby"
date: "2/9/2018"
output: html_document
---

```{r setup, include=FALSE}
## graphics
library(ggplot2)
theme_set(theme_bw()+theme(panel.spacing=grid::unit(0,"lines")))
library(directlabels)
## modeling/coef plots
library(lme4)
library(broom)
library(dotwhisker)
library(ggstance) ## horizontal geoms
## manipulation
library(tidyr)
library(dplyr)
library(purrr)
library(readr)
library(cowplot)
library(directlabels)
```

The data I am using I got from Statistics Canada. This data is the incidence of cancers in various provinces from 2011 to 2015. 

```{r}
data<-read.csv("cancer.csv")

names(data)<-c("Geography", "Characteristics", "2011", "2012", "2013", "2014", "2015")

data[9,1]<-"Ontario" ##cleaning up data

data$Characteristics <- as.character(data$Characteristics)

data$Characteristics[data$Characteristics == "Cancer incidence (rate per 100,000 population) (24)"] <- "Incidence"

data<-data[which(data$Characteristics == "Incidence"),]

data$Characteristics <- NULL

data1<- data %>% 
  gather(Year, Cases, -Geography)

```

```{r}
gg1<-( ggplot(data1, aes(Year, Cases, col=Geography)) +
        geom_point() + 
        geom_line(data=data1,aes(group=Geography)) + 
        geom_dl(aes(label=Geography), method = list("last.points")) + 
         theme(legend.position="none") + 
         labs(x="Year", y="Incidence (per 100,000)")
)
plot(gg1)
```

I would say this graph is much better than the data provided. It is immediately clear which provinces have a low incidence of cancer and which provinces have a high incidence of cancer. One would not be able to gather this information in a reasonable amount of time from reading the graph. Another thing that is obvious from the graph that wouldn't be obvious from the data is that there isn't much change in the incidence across provinces. 

I was wondering how I could spread the names out so they aren't overlapping? Could you help me with that?